\chapter{Steam\+OS }
\hypertarget{md__mono_runtime_2extern_2sdl_2docs_2_r_e_a_d_m_e-steamos}{}\label{md__mono_runtime_2extern_2sdl_2docs_2_r_e_a_d_m_e-steamos}\index{SteamOS@{SteamOS}}
\label{md__mono_runtime_2extern_2sdl_2docs_2_r_e_a_d_m_e-steamos_autotoc_md1447}%
\Hypertarget{md__mono_runtime_2extern_2sdl_2docs_2_r_e_a_d_m_e-steamos_autotoc_md1447}%


Steam\+OS is literally a Linux system, and uses the same binaries you distribute to generic Linux Steam users, so generally speaking, all the other \doxysectlink{md__mono_runtime_2extern_2sdl_2docs_2_r_e_a_d_m_e-linux}{Linux advice}{0} applies.

If you are shipping a Linux game on Steam, or explicitly targeting Steam\+OS, the system is guaranteed to provide SDL. The Steam Client will set up the dynamic loader path so that a known-\/good copy of SDL is available to any program that needs it before launching a game. Steam provides all major versions of SDL to date, in this manner, for both x86 and amd64, in addition to several add-\/on libraries like {\ttfamily SDL\+\_\+image} and {\ttfamily SDL\+\_\+mixer}. When shipping a Linux game on Steam, do not ship a build of SDL with your game. Link against SDL as normal, and expect it to be available on the player\textquotesingle{}s system. This allows Valve to make fixes and improvements to their SDL and those fixes to flow on to your game.

We are obsessive about SDL3 having a backwards-\/compatible ABI. Whether you build your game using the Steam Runtime SDK or just about any other copy of SDL, it {\itshape should} work with the one that ships with Steam.

In fact, it\textquotesingle{}s not a bad idea to just copy the SDL build out of the Steam Runtime if you plan to ship a Linux game for non-\/\+Steam platforms, too, since you know it\textquotesingle{}s definitely well-\/built. 